\papertitle

### 2017-06-08 paper/paper.tex
Added non-integer bin differences. Need to check why it behaves weirdly
when rounding because it worked okay without rounding, which must just use the floor, no?

Also working on drawing flow chart to describe evaluation procedure but having difficulty specifying edges with
corners.

@@

\section{A continuous window design example}
\label{sec:designexample}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{comp_offset_chirp_est_err_params}.eps}}
\caption{\label{fig:mixwincomp} The mean squared estimation error for each
    parameter in an analysis of two components in mixture. A set of
    $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
    maximum bin differences $0 \leq d < \Doffset{}$. The signal power ratio
    between components is indicated with colours and the corresponding ratio in decibels is indicated in the
    plot legend. The names indicate the windows used to generate the atoms for
    estimation: \textit{N3} and \textit{N4} are the 3- and 4-cosine-term
    continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
is the continuous 5-cosine-term approximation to a digital prolate window as
described in Sec.~\ref{sec:designexample}.}
\end{figure*}
%
As a design example we show how to create a continuous approximation of a digital
prolate spheroidal window.

@@

To compare the average estimation error variance with the
theoretical minimum given by the Cram\'{e}r-Rao bound we synthesized $K_{1}$ random
chirps using Eq.~\ref{eq:polyphaseexp}
with $Q=2$ and parameters chosen from uniform distributions justified in
\cite{betser2009sinusoidal}. The original Hann window,
the windows proposed by Nuttall and the new digital prolate based window were
used to synthesize the atoms as described in Sec.~\ref{sec:designingatoms} and
their estimation error variance was compared (see
Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
with the atoms, the three atoms whose inner products were greatest were used in
the estimations, i.e., $R=3$ in Eq.~\ref{eq:ddmsyseq}. We see that windows with
lower sidelobes exhibit the lowest possible error variance at the sacrifice of
some estimator efficiency.

To evaluate the performance of the various windows when estimating the
parameters of components in mixture we synthesized signals using
Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
uniform distributions specified in \cite{betser2009sinusoidal}.  We desired to
see how the accuracy of estimation is influenced by the difference (in bins)
between the locally maximized atoms and the difference in signal power between
the two components. To obtain a set of components from which test signals
exhibiting the desired differences could be constructed, we synthesized a set
$\mathcal{C}$ of $K_{2}$ components for which the energy is maximized in bin 0.
Test signals were obtained by choosing a pair of unique components from this set
and modulating one to give the desired difference.  This was carried out as
follows: the atom $r^{\ast}$ for which the inner product was maximized was
determined for each unmixed chirp and the chirp was modulated by $\exp(-2\pi
\frac{r^{\ast} n}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to move this maximum
to $r=0$. Then for each desired difference $d$, with $0 \leq d < D$, two unique
chirps were selected from $\mathcal{C}$ and one chirp was modulated by
$\exp(2\pi \frac{n d}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to give the
desired difference between maxima. This component was also scaled by a constant
to give a desired signal power ratio with the other component (the power ratios
tested were 0 dB and -30 dB). The parameters of
both components were estimated using the bins surrounding $r=0$ and $r=d$ for
each component respectively and the squared estimation error for each parameter
was summed and divided by $K_{2}(K_{2}-1)$ (the number of choices of two unique
components) to give the averaged squared estimation error for each parameter at
each difference $d$.

>>>>

% Flowchart drawing stuff
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\tikzstyle{startstop} = [rectangle,draw=black,text centered]%, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text
centered, draw=black, text width=3cm]
\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\section{A continuous window design example}
\label{sec:designexample}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{comp_offset_chirp_est_err_params}.eps}}
\caption{\label{fig:mixwincomp} The mean squared estimation error for each
    parameter in an analysis of two components in mixture. A set of
    $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
    maximum bin differences $0 \leq d < \Doffset{}$, with $d$ varied in
    $\Dstep{}$ bin increments. Only local maxima are plotted for clarity. The signal power ratio
    between components is indicated with colours and the corresponding ratio in decibels is indicated in the
    plot legend. The names indicate the windows used to generate the atoms for
    estimation: \textit{N3} and \textit{N4} are the 3- and 4-cosine-term
    continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
is the continuous 5-cosine-term approximation to a digital prolate window as
described in Sec.~\ref{sec:designexample}.}
\end{figure*}
%
As a design example we show how to create a continuous approximation of a digital
prolate spheroidal window.

@@

To compare the average estimation error variance with the
theoretical minimum given by the Cram\'{e}r-Rao bound we synthesized $K_{1}$ random
chirps using Eq.~\ref{eq:polyphaseexp}
with $Q=2$ and parameters chosen from uniform distributions justified in
\cite{betser2009sinusoidal}. The original Hann window,
the windows proposed by Nuttall and the new digital prolate based window were
used to synthesize the atoms as described in Sec.~\ref{sec:designingatoms} and
their estimation error variance was compared (see
Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
with the atoms, the three atoms whose inner products were greatest were used in
the estimations, i.e., $R=3$ in Eq.~\ref{eq:ddmsyseq}. The windows with the
lowest sidelobes only give the lowest error variance at very favourable SNRs, at
real-world SNRs the original Hann window still performs best at estimating the
parameters of a single component signal.

\begin{tikzpicture}[node distance=2cm]

    \node (start) [process] {Synthesize $K_{2}$ single-component signals};
    \node (modulate) [process, below of=start] {Modulate down so peak bin is at frequency 0 for all signals};
    \node (setd) [process, below of=modulate] {Set $d=0$};
    \node (choosepair) [process, below of=setd] {Choose pair of signals};
    \node (scaleone) [process, below of=choosepair] {Scale one in the pair to give desired power and peak bin according to $d$};
    \node (addpair) [process, below of=scaleone] {Add pair together};
    \node (tryestimate1) [process, below of=addpair] {Try estimating parameters of component with atoms at bins $\{-1,0,1\}$};
    \node (tryestimate2) [process, below of=tryestimate1] {Try estimating parameters of component with atoms at bins $\{\hat{d}-1,\hat{d},\hat{d}+1\}$};
    \node (sumerrs) [process, below of=tryestimate2] {Sum estimation errors of
    each parameter and divide by $K_{2}(K_{2}-1)$};
    \node (incd) [process, below of=sumerrs] {Increment $d$ by $\Dstep{}$ unless $d=\Doffset$};

    \draw [arrow] (start) -- (modulate);
    \draw [arrow] (modulate) -- (setd);
    \draw [arrow] (setd) -- (choosepair);
    \draw [arrow] (choosepair) -- (scaleone);
    \draw [arrow] (scaleone) -- (addpair);
    \draw [arrow] (addpair) -- (tryestimate1);
    \draw [arrow] (tryestimate1) -- (tryestimate2);
    \draw [arrow] (tryestimate2) -- (sumerrs);
    \draw [arrow] (sumerrs) -- (incd);
    \draw [arrow] (incd) -- node[anchor=east,above]{} (choosepair);

\end{tikzpicture}

To evaluate the performance of the various windows when estimating the
parameters of components in mixture we synthesized signals using
Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
uniform distributions specified in \cite{betser2009sinusoidal}.  We desired to
see how the accuracy of estimation is influenced by the difference (in bins)
between the locally maximized atoms and the difference in signal power between
the two components. To obtain a set of components from which test signals
exhibiting the desired differences could be constructed, we synthesized a set
$\mathcal{C}$ of $K_{2}$ components for which the energy is maximized in bin 0.
Test signals were obtained by choosing a pair of unique components from this set
and modulating one to give the desired difference.  This was carried out as
follows: the atom $r^{\ast}$ for which the inner product was maximized was
determined for each unmixed chirp and the chirp was modulated by $\exp(-2\pi
\frac{r^{\ast} n}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to move this maximum
to $r=0$. Then for each desired difference $d$, with $0 \leq d < D$, two unique
chirps were selected from $\mathcal{C}$ and one chirp was modulated by
$\exp(2\pi \frac{n d}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to give the
desired difference between maxima. This component was also scaled by a constant
to give a desired signal power ratio with the other component (the power ratios
tested were 0 dB and -30 dB). Because the estimation must use valid atom
indices, $d$ was rounded to the nearest integer $\hat{d}$. The parameters of
both components were estimated using the bins surrounding $r=0$ and $r=\hat{d}$ for
each component respectively and the squared estimation error for each parameter
was summed and divided by $K_{2}(K_{2}-1)$ (the number of choices of two unique
components) to give the averaged squared estimation error for each parameter at
each difference $d$.
